\clearpage
\phantomsection

\addcontentsline{toc}{chapter}{Abstract}
\chapter*{\fontsize{13}{13}\selectfont{Abstract}}
\fontsize{12}{12}\selectfont{
\noindent\textbf{Abstract:}
The rapid growth of the global Anime/Manga market, coupled with the increasing demand for AI-powered content creation tools, has driven research into the problem of converting real-person portraits to 2D anime style (photo-to-anime). This task offers significant application potential but poses many challenges regarding image quality, facial identity preservation, and training stability. Previous approaches such as Neural Style Transfer and CycleGAN often suffer from noise, artifacts, and slow processing speed.

This thesis investigates, reproduces, and extends the AnimeGANv3 model based on the Double-Tail GAN (DTGAN) architecture -- a next-generation Generative Adversarial Network (GAN) employing a dual-branch Generator (Support Tail and Main Tail), Linearly Adaptive Denormalization (LADE), External Attention v3, and a specialized loss system combining adversarial loss, content loss (based on VGG19), style loss, color loss, and region smoothing loss. The main contribution of this thesis is the design and integration of a Face Mode module using RetinaFace MobileNet 0.25 combined with a Margin Expansion algorithm, forming a complete pipeline: face detection $\rightarrow$ face region cropping and expansion $\rightarrow$ high-quality anime conversion.

The model was trained on the vast.ai cloud computing platform using two unpaired datasets consisting of real-person portraits and anime images in the styles of Hayao Miyazaki and Makoto Shinkai. The two-phase training process (5 epochs of pre-training and 69 epochs of adversarial training) demonstrated stable convergence. Experimental results achieved FID $= 58.6$ and LPIPS $= 0.384$ in Face Mode -- outperforming CycleGAN, CartoonGAN, and AnimeGANv2. The Face Mode module improved FID by approximately $8.7\%$ compared to Landscape Mode. The ONNX model is only 9.1 MB and achieves 42 FPS at $256 \times 256$ on GPU. The system was deployed as a complete web application (React frontend and FastAPI backend), supporting both image and video conversion. The thesis also proposes future development directions including face alignment, face blending, temporal consistency for video, and multi-style expansion.

\vspace{0.5cm}
\noindent\textit{\textbf{Keywords:}} \textit{GAN, AnimeGANv3, DTGAN, image style transfer, portrait, anime style, LADE, RetinaFace, Face Mode, ONNX.}
}